### 2017-09-06 paper/evaluation.tex
Removed a comment
Minor fixes from past review

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory and \SubjectsGithubNotTestable{}
projects were unable to test due to incompatible environment (\eg,
missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with
non-deterministic test results.
In general, a test that either pass or fail under the same circumstances
is known as a ``flaky test''~\cite{luo-etal-fse2014}.
\Comment{While there are several causes that may introduce randomness on test
results, our concern is on flakiness caused by
parallel execution.}
As some of our experiments consist in running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
\Jbc{From the \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with more than \SuiteFailingThreshold{} of tests failing to
reduce bias in our dataset.}
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.25\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} projects unable to test,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.}
\end{figure}

@@

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to process the
data and generate plots.  All source artifacts are publicly available
for replication (on our website~\cite{ourwebpage}).  This
includes supporting scripts (\eg, the script that test subjects and
generates raw analysis data) and the full list of projects. \Comment{,
  and a \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

@@

We took the following actions to isolate our environment from
measurement noise.  First, we observed that some test tasks called
test-unrelated tasks (\eg, \emph{javadoc} generation and static
analyses) that could interfere in our time measurements.  To address
that potential issue, we inspected Maven execution logs from a sample
including a hundred projects prior to running the script from
Figure~\ref{fig:mvn-execution}.  The tasks we found were ignored from
execution (lines 1-4).  Furthermore, to avoid noise from operating
system events, we configured our workstation to run only essential
services.  The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{} group), tests that run in one to five minutes (\medg{}
group), and tests that run in five or more minutes (\longg{}
group). We followed a similar methodology to group projects by time as
Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
regression test selection.\Comment{ and added the \medg{} group due to
  the variability of the time cost from subjects out of the \shortg{}
  group} Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As expected, \longg{} and \medg{} projects do not occur
as frequently as \shortg{} projects.  However, they do occur in
relatively high numbers.

Figure~\ref{fig:rq1-boxplot} shows cost distribution of test suites in
each group as boxplots.  Note that the y-ranges are different.  The
distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
  group}.  The test suites in this group ran in 15 or less seconds for
over 75\% of the cases.  Such scenarios constitute the majority of the
cases we analyzed.  Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take over 3.5 minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes over 50 minutes
to complete, as can be observed from the outliers (dots) in the plot.

@@

It is important to note that we under-estimated cost in our
experiments for one main reason.
Some projects may omit long-running tests on their default
execution. For instance, the project \CodeIn{apache.maven-surefire}
runs all unit tests in a few seconds.  According to our criteria, this
project is to be classified as \shortg{} but a closer look reveals
that only smoke tests are run by default in this project.
Time-consuming integration and system tests are only accessible via
custom parameters, which we do not handle in our experimental setup.
We enabled such parameters for this specific project and observed that
testing time goes to nearly 30 minutes.  For simplicity, we considered
only the tests executed by default.
\Jbc{
Although failing tests may introduce noise in our measurements, we
carefully eliminated subjects with more than \SuiteFailingThreshold{} of
test failures. 
From the \numSubjs{} testable projects, \numSubjsPass{} successfully
executed all tests and \numSubjsFail{} reported some test failure.
Furthermore, from these \numSubjsFail{} subjects, only 11 subjects
have more than 5\% of failing tests (7.3\% in average).
}
\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, over 1 in every 5
      projects) take at least 1 minute to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  We noted a small number of
cases of CPU monopolization.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
\longg{} group.  This project contains only 26 tests, 17 of which take
less than 0.5s to run, one of which takes nearly 3s to run, two of
which take nearly 11s to run, four which takes in average 3m to run, and two of
which take $\sim$8m to run.  For this project, 98.4\% of the
execution cost is dominated by 20\% of the tests; without these
two costly tests this project would have been classified as
short-running.
We did not find other projects with such extreme time monopolization
profile.
Project \CodeIn{facebookarchive\_linkbench} is also classified as
long-running and has the second highest value of $\sigma$.
For this project, however, cost is distributed more smoothly across 98
tests, of which 8 (8.1\%) take more than 1s to run with the rest of
the tests running faster.

@@

Figure~\ref{fig:time-distributions} shows that the average median
times are similar for \medg{} and \longg{}-running test suites.
The difference in overall running times of projects in those groups
is mainly justified by the number of test cases as opposed to the
individual costs of test cases.
Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.  This figure indicates
that long projects, albeit having a wider inter-quartile range (middle
50\% projects in this group are less predictable), have a higher
median and much higher average number of test cases.  Furthermore, we
noted a strong positive correlation between running time and number of
test on projects in the \longg{} group.  Considering the \medg{}
group, the correlation between these two variables was weak.
Figure~\ref{fig:scattercost} illustrates this regression line.

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupOne{}:}~\emph{Considering the
      machine setup we used, the average speedup observed with default
      configurations of parallelization was \avgSpeedup{}x.
      \Jbc{The design of the test suite impacts the speedup obtained
      in a given parallel configuration.}
      }
  \end{minipage}
}
\end{center}

>>>>

From these \SubjectsGithub{} downloaded projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, and we were unable to test
\SubjectsGithubNotTestable{} projects  due to incompatible environment
(\eg, missing required web browser or database management system).
In addition, we identified \SubjectsGithubFlaky{} projects with
``flaky tests''~\cite{luo-etal-fse2014}.
In general, a ``flaky test'' is a test that either pass or fail under
the same circumstances leading to non-deterministic results.
\Comment{While there are several causes that may introduce randomness on test
results, our concern is on flakiness caused by
parallel execution.}
As some of our experiments consist in running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
\Jbc{From the \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with more than \SuiteFailingThreshold{} of tests failing to
reduce bias in our dataset.}
Our final set of subjects consists of \numSubjs{} projects.
Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.27\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.}
\end{figure}

@@

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include Git, Java 8, and Maven
3.3.9.
We used Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to
process test results and generate plots.  All source artifacts are
publicly available for replication on our website~\cite{ourwebpage}.
This includes supporting scripts (\eg, the script that test subjects
and generates raw analysis data) and the full list of projects.
\Comment{, and a \emph{Vagrantfile} to emulate our hardware and all
software dependencies.}

@@

We took the following actions to isolate our environment from
measurement noise.
First, we observed that some test tasks called test-unrelated tasks
(\eg, \emph{javadoc} generation and static analyses) that could
interfere in our time measurements.
To address that potential issue, we inspected Maven execution logs
from a sample including a hundred projects prior to running the script
from Figure~\ref{fig:mvn-execution}.
The tasks we found were ignored from execution (lines 1-4).
Furthermore, to avoid noise from unrelated OS events, we configured
our workstation to only run essential services.
The machine was dedicated to our experiments and we
accessed it via SSH. In addition, we configured the \CodeIn{isolcpus}
option from the Linux Kernel \cite{linux-kernel} to isolate six
virtual CPUs to run our experiments, leaving the remaining CPUs to run
OS processes~\cite{isolcpus-use}.  The rationale for this decision is
to prevent context-switching between user processes (running the
experiment) and OS-related processes.  Finally, to make sure our
measurements were fair, we compared timings corresponding to the
sequential execution of tests using Maven with that obtained with
JUnit's default \CodeIn{JUnitCore} runner, invoked from the command
line.  Results were very close.

@@

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{} group), tests that run in one to five minutes (\medg{}
group), and tests that run in five or more minutes (\longg{}
group).
\Comment{We followed a similar methodology to group projects by time as
Gligoric~\etal{}~\cite{gligoric-etal-issta2015} in their work on
regression test selection.}
\Comment{ and added the \medg{} group due to the variability of the
time cost from subjects out of the \shortg{} group}
Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As expected, \longg{} and \medg{} projects do not occur
as frequently as \shortg{} projects.  However, they do occur in
relatively high numbers.

Figure~\ref{fig:rq1-boxplot} shows as boxplots distribution of cost of
test suites in each group.
Note that the y-ranges are different.
The distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
group}.
The test suites in this group ran in 15 or less seconds for
over 75\% of the cases.  Such scenarios constitute the majority of the
cases we analyzed.  Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take 3.5 or more minutes to run and nearly 75\% of
the projects from the \longg{} group took $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes over 50 minutes
to complete, as can be observed from the outliers (dots) in the plot.

@@

It is important to note that we under-estimated cost in our
experiments for one main reason.
Some projects may omit long-running tests on their default
execution. For instance, the project \CodeIn{apache.maven-surefire}
runs all unit tests in a few seconds.  According to our criteria, this
project is classified as \shortg{} but a closer look reveals
that only smoke tests are run by default in this project.
Time-consuming integration and system tests are only accessible via
custom parameters, which we do not handle in our experimental setup.
We enabled such parameters for this specific project and observed that
testing time goes to nearly 30 minutes.  For simplicity, we considered
only the tests executed by default.
\Jbc{
Although failing tests may introduce noise in our measurements, we
carefully eliminated subjects with more than \SuiteFailingThreshold{} of
test failures. 
From the \numSubjs{} testable projects, \numSubjsPass{} successfully
executed all tests and \numSubjsFail{} reported some test failure.
Furthermore, from these \numSubjsFail{} subjects, only 11 subjects
have more than 5\% of failing tests (7.3\% in average).
}
\vspace{1ex}
\begin{center}
\fbox{
\begin{minipage}{8cm}
    \textit{Answering \numRQFeasibilityOne{}:}~\emph{We conclude that
      time-consuming test suites are relatively frequent in
      open-source projects.  We found that \percentMedLongRunning{} of
      the \numSubjs{} projects we analyzed (\ie{}, nearly 1 in every 4
      projects) take at least 1 minute to run and
      \percentLongRunning{} take at least 5 minutes to run.\Comment{
        (\ie, \numMedLong{} projects from \medg{} and \longg{}).}}
\end{minipage}
}
\end{center}
\vspace{1ex}

@@

\sloppy Figures~\ref{fig:longtcost} and~\ref{fig:medtcost} show the
time distribution of individual test cases per project.  We observed
that the average median value of execution cost for a test was
relatively small (dashed horizontal red lines), namely 0.31s for
\medg{} projects and 0.23s for \longg{} projects.  The standard
deviations associated with each distribution were relatively
low.\Comment{ Figure~\ref{fig:sd} shows the number of projects within
  specific ranges of $\sigma$ values.}  We noted a small number of
cases of CPU monopolization.  For example, the highest value of
$\sigma$ occurred in \CodeIn{uber\_chaperone}, a project from the
\longg{} group.  This project contains only 26 tests, 17 of which take
less than 0.5s to run, one of which takes nearly 3s to run, two of
which take nearly 11s to run, four of which takes on average 3m to run, and two of
which take $\sim$8m to run.  For this project, 98.4\% of the
execution cost is dominated by 20\% of the tests; without these
two costly tests this project would have been classified as
short-running.
We did not find other projects with such extreme time monopolization
profile.
Project \CodeIn{facebookarchive\_linkbench} is also classified as
long-running and has the second highest value of $\sigma$.
For this project, however, cost is distributed more smoothly across 98
tests, of which 8 (8.1\%) take more than 1s to run with the rest of
the tests running faster.

@@

Figure~\ref{fig:time-distributions} shows that the average median
times are similar for \medg{} and \longg{}-running test suites.
The difference in overall running times is mainly justified by the
number of test cases as opposed to the individual costs of test cases.
Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.  This figure indicates
that long projects, albeit having a wider inter-quartile range (middle
50\% projects in this group are less predictable), have a higher
median and much higher average number of test cases.  Furthermore, we
noted a strong positive correlation between running time and number of
test on projects in the \longg{} group.  Considering the \medg{}
group, the correlation between these two variables was weak.
Figure~\ref{fig:scattercost} illustrates this regression line.

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupOne{}:}~\emph{Considering the
      machine setup we used, the average speedup observed with default
      configurations of parallelization was \avgSpeedup{}x.
      }
  \end{minipage}
}
\end{center}
